Results

### 2023-02-21 06_Paper/ER-ED/ERED_Stage2/Results.Rmd
added ordinal regression results

To investigate the ecological validity of the subjective values of ER strategies we calculated, we looked to see if SVs were associated with the actual choice of participants in the choice block.
Therefore, a $\chi^{2}$ test with predicted choice (i.e., the strategy with the highest SV of each participant) and actual choice was computed.
There was a significant association between predicted choice and actual choice (`r papaja::apa_print(choice_chisq, n=120)$statistic[[1]]`, `r papaja::apa_print(choice_chisq_BF)$statistic`).

[ HIER FEHLT NOCH DIE ORDINALE REGRESSION ]

>>>>

To investigate the ecological validity of the subjective values of ER strategies we calculated, we looked to see if SVs were associated with the actual choice of participants in the choice block.
Therefore, a $\chi^{2}$ test with predicted choice (i.e., the strategy with the highest SV of each participant) and actual choice was computed.
There was a significant association between predicted choice and actual choice (`r papaja::apa_print(choice_chisq, n=120)$statistic[[1]]`, `r papaja::apa_print(choice_chisq_BF)$statistic`). 
We then conducted a ordinal regression with the dependent variable "choice" and the individual SVs of all three strategies as independent variables.
Overall model fit was fair with $R^{2}=$ `r papaja::printnum(Choice_OrdReg_R2)`.
The predictor SV of strategy distraction was found to contribute to the model (`r papaja::apa_print(Choice_OrdReg)$estimate$distraction_sv`).
